\hspace{1cm}\\[5cm]
{\huge Abstract}
\\\HRule\\

Simplesite is a danish web-hosting company based in Copenhagen. They recently
switched to a freemium based business model and stopped deleting inactive
websites entirely in a bid to have more users stay with them. This have lead to
a great influx of new customers using the free version of their services, many
of which open a free website with their service but do not stay active for very
long. Simplesite wishes to improve the situation by first getting users to stay
active for longer, and at a later date try to make the active users become
paying customers.

In order to gain a better understanding of what make some customers stay and
others not, a business problem is formulated and converted to a data science
problem; ``\textit{Is it possible to find any differences between customers who
are active on day 15 and later, and customers who leave before?}'' Through the
course of the report this problem is worked on using the Cross Industry Standard
Process for Data Mining (CRISP-DM); the business problem is converted into a
data science problem, I describe the available data and reason about
modifications to the datasets before creating and validating different models in
order to produce the best possible model. After the model have been created it
is evaluated and the process starts over.

The project went through several iterations of the CRISP-DM process, and each
iteration is covered and reasoned about. The results are evaluated and
suggestions for improvements and implementation ideas are outlined for future
work.

The models developed during the project show that for the currently available
data, two attributes are the most important for predicting if a customer is
retained or not; the number of logins and the number of edits during the first
14 days.

Finally the report contains my reflections on how my education have been used in
this company project and how the academic diciplines have I have been taught at
DIKU have been applied or expanded during the project.
