\section{Simplesite ApS}

Simplesite is a danish website/hosting company that was founded as \textit{Elk
Consulting ApS} in 2001 by Morten and Jacob Elk \cite{cvr2016simplesite}. In
2003, the company changed its name to \textit{123Hjemmeside ApS} in order to
reflect the product they delivered. Over the years, as 123hjemmeside expanded
into new countries, the name was translated into the local equivelant for each
version of the site. In 2014, 123hjemmeside adopted its secondary name
\textit{Simplesite ApS} as its new primary name in order to unify all it its
brands under a single name.

The information in this section is gathered from \cite{cvr2016simplesite},
interviews with and from having worked in the operations department for 5 years.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Product}

Simplesite produce and maintain an inhouse website Content Management System
(CMS) and operate a hosting location where this CMS runs. Apart from the full
paid version, customers can register for a free account allowing them to host a
website that is edited through the CMS. The free accounts are under restrictions
on number of pages, images and videos that can be added to the site. Customers
can then change to a paid subscription which allows them to have more pages,
images and videos on their website.

Simplesite also offer additional services to their customers that can be bought
for an extra fee if you are already a paying customer, this includes the ability
to have a domain attached to your website, a webshop as well as additional
pages, images and videos.

The product is hosted partially on Simplesites own hardware in an offsite
location, and using a number of cloud services to provide faster response times
for certain data types.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Departments}

The employees work from three different offices located in Denmark, Bulgaria and
Serbia, but also have people working from other locations around the world.

\begin{itemize*}
    \item \textbf{Administration} - Situated at the ground floor of the
          Copenhagen office, this department contains the HR functions as well
          as finance.

    \item \textbf{Sales} - Also on the ground floor of the Copenhagen office,
          sales consists of full time employeess and student helpers. The
          primary task is to sell the product, currently through localized ad
          management.

    \item \textbf{Product \& Communication} - The department
          sits on the upper floor of the Copenhagen office and is responsible
          for planning new features in cooperation with the developers as well
          as manage content on Simplesites own websites. P \& C also manages
          communication such as newsletters and localized ad texts.

    \item \textbf{In-House Development} - Sitting next to P \& C on the upper
          floor the developers are responsible for implementing new features as
          well as maintenence, analytics and bug fixing of the product.

    \item \textbf{Operations} - Daily operations are handled primarily by the
          company CTO, Thomas, as well as 2 part time students. Operations sits
          on the upper floor in Copenhagen next to the developers.

    \item \textbf{Support} - Since the product is offered in several languages,
          a supporter is hired per language in a part time basis. All supporters
          work from home but get together once a month for a status meeting and
          to make sure new knowledge is shared and that relevant information can
          be given from the regular departments.

    \item \textbf{Remote Dev 1} - A small number of developers work in
          Bulgaria and have their own office in the Sofia, they are offered
          machines in the Copenhagen office they can VPN into and use for work.
          This allows the operations department to work from Copenhagen and
          still service the remote developers.

    \item \textbf{Remote Dev 2} - A number of developers work from
          Serbia, like the remote developers in Bulgaria, they also VPN into the
          Copenhagen office and work on machines maintained by the regular
          operations employees.

    \item \textbf{Miscellaneous} - Simplesite also occasionally employs external
          specialists or consultants. Depending on the need, they will either
          work in the Copenhagen office or from some remote location using VPN.
\end{itemize*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Company Structure}

Figure \ref{fig:organization} shows the overall organization of Simplesite. For
simplicity I have merged the remote development offices into the ``regular''
development department since they occupy the same space in the organization, the
only difference is the geographical seperation.

\begin{landscape}
  \graphicc{1.5}{img/organization_01}{Organizational diagram for Simplesite ApS,
    text in bold represents departments. Last names are omitted to keep the
    figure small.}{fig:organization}
\end{landscape}