\section{Problem Analysis}

In order to work with the the problem described in Section \ref{sec:probdesc} I
used a workflow called called the \textit{Cross Industry Standard Process for
Data Mining}, shortened to CRISP-DM (as described in \cite[p.
26]{provost2013data}, originally from \cite{shearer2000crisp}). An overview of
the process can be seen in Figure \ref{fig:crisp}. The following subsections
will go over each phase in the process, explaining what the purpose of the phase
is and cover my work during that phase of the project.

\graphicc{0.8}{img/wiki_crisp}{Diagram of the CRISP-DM method. Source:
  \cite{wiki2016crisp}.}{fig:crisp}

Simplesite have performed most of the \textit{business understanding} step so
the work I performed is placed in \textit{data understanding}, \textit{data
preparation}, \textit{modelling} and \textit{evaluation}. Due to the short
duration of the project, there have not been any time spent with the
\textit{deployment} phase.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Business Understanding}

The business understanding phase is the entry point for most data science
projects, it covers the process of taking a business project, and converting it
to a data science project. My work in the phase have been very limited, since
Simplesite had a very clear idea of what they would like to investigate first.
The initial business problem for this project can be described as ``\textit{We
have a large number of free users, but a lot of them do not stay with the
product. Can we find out why?}''. From this business problem it makes sense to
ask ``\textit{Can we find a difference between the customers that stay and those
who don't?}'', more specifically is there a difference in the way the customer
behave when using the site? And that question is what this project is being
performed from.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{03_00_dataunderstand}
\input{03_01_datapepare}
\input{03_02_model}
\input{03_03_evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Deployment}

In the deployment phase of the process, the results from the data mining is used
to either implement changes to the system that the modelling uncovered or
implement the model itself into a workflow that allow it to be resued with new
data later.

Due to the time restrictions and the fact that the results of the project is
published for the first time in this report, the deployment phase of the CRISP-
DM process will be taking place after the end of the project. For the final
results and ideas for future work, see Section \ref{sec:results}.
